Group Signatures Meet Anonymous Credentials: Or, How to Build Privacy Preserving Identities with Accountability

### 2022-02-26 prism-backend/research/gsac/uas-model.tex
Seemingly complete definition! Working on textual descriptions.

@@

\commentwho{Jesus}{I'm trying to define \Sign, \Verify, \Inspect and \Judge such
  that multiple credentials can be used to produce a single signature, proving
  claims over arbitrary subsets of all the credentials owned by a user. \Verify
  and, consequently, \Inspect and \Judge need to receive all the \gpk's.
  \Inspect only requires one inspector's secret key, though, and will thus only
  produce that inspector's function of the signature and message (this is to
  avoid complex interactive protocols between many inspectors). This, however,
  creates a quite annoying syntax. If this becomes unmanageable, it may just be
  easier to restrict signatures to claims over the attributes contained in
  \emph{one} credential.}

@@

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. Hereafter, we assume that the
  public part \ipk is added to the group public key \gpk, as well as \fissue.
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers). Hereafter, we assume that the
  public part \opk is added to the group public key \gpk, along with \finsp.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\attrs,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})
  \rangle$.] %
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred from an issuer in the system, on
  attribute set $\attrs$ plus, possibly, blinded attributes attested by
  previously obtained credentials $\cred_i$, from a multiset of other issuers
  (which may include the one to whom a new credential is being requested) with
  public keys $\gpk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\gpk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$\sig \gets \Sign(\usk,\msg,\feval,
  \ldblbrace (\gpk_i,\cred_i)\rdblbrace_{i \in \Issuers})$.]
  The user with with secret key \usk, who obtained credentials $\cred_i$ from a
  multiset of issuers in the system, produces a signature \sig over message
  \msg, meeting the conditions defined by \feval. As in \Obtain and \Issue, we
  omit the credentials' group public keys when possible.
\item[$1/0 \gets
  \Verify(\sig,\msg,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.]
  Checks whether \sig is a valid signature, over message \msg.
\item[$(\y,\iproof)/\bot \gets \Inspect(\osk,\trans,\sig,\msg,
  \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.] %
  Executed by the inspector with private key \osk. Receives a signature \sig
  over message \msg, produced by a set of credentials endorsed by a multiset of
  issuers with public keys $\gpk_i$. If \trans contains a set of valid
  transcripts corresponding to the $\langle\Obtain,\Issue\rangle$ interactive
  protocol executions that issued one or more credentials used to produced \sig,
  the function outputs a value $\y$ derived from the signer's public key,
  credentials, message, and signature, as well as a proof of correct inspection.
  We sometimes abuse notation, and write $\trans[\uid]$ to mean that the \Inspect
  function is operating only for the obtain transcripts related to user \uid. 
\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,
  \ldblbrace \gpk_i\rdblbrace_{i \in \Issuers})$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \y,
  obtained by applying \Inspect to the the signature \sig over message \msg. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\upk, \attrs,\scred) \rightarrow 0/1$.] Defined by issuers,
  governs what customized conditions an issuer requires in order to issue
  credentials, when receiving a request from user with public key \upk, for
  attributes \attrs. \fissue may run checks on a (possibly empty) set of
  additional credentials \scred, which may further be used for blind issuance
  \commentwho{Jesus}{can it?}. \fissue returns $1$ to accept a request, $0$ to
  reject it.  
\item[$\feval: (\upk,\scred,\msg) \rightarrow 0/1$.] Can be defined by any party,
  although we anticipate that this will typically be done by either singers,
  verifiers, or some governance organization. It defines customized conditions
  to be met by the owner of a user key \upk and set of credentials \scred, in
  order to sign a concrete message \msg. Returns $1$ to allow the signing,
  or $0$ to disallow it.
\item[$\finsp: (\upk,\scred,\msg,\sig) \rightarrow \bin^*$.] Defines what
  utility value, derived from the user's public key, credentials, signed
  message, and produced signature (or a subset thereof), should be extractable
  by the group inspector.
\end{description}

@@

\begin{description}
\item[Tables for parties]:
  \begin{description}
  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
    i.e., they are sets of {\uid}s.
  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers.
    Since we assume only one issuer per group, they are sets of {\gid}s.
  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) inspectors.
    Since we assume only one inspector per group, they are sets of {\gid}s.
  \end{description}
\item[Tables for keys]:
  \begin{description}
  \item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$.
    To refer to the key pair of a specific user, we use $\UK[\uid]$. \PUBUK
    is a shorthand to refer to the public part, and \PRVUK refers to the
    private part -- we may also index both by \uid.
  \item[\IK, \PUBIK and \PRVIK.] Same as \UK, but for issuer key pairs. In
    addition, \IK also includes the \fissue function, which is part of the
    public key.
  \item[\OK, \PUBOK, \PRVOK.] Same as \UK, but for inspector key pairs. In
    addition, \OK also includes the \finsp function, which is part of the
    public key.
  \item[\GK.] We bundle public keys for issuers and inspectors into a common
    public key for each group. We use the table \GK for that purpose which,
    consequently, can also be indexed by \gid.
  \end{description}
\item[Tables for credentials-related data]:
  \begin{description}
  \item[\CRED.] Stores credentials obtained by honest users. Thus, it is
    indexable by \cid. However, we slightly abuse notation and also use
    $\CRED[\uid]$ as a shorthand for all credentials obtained by honest user
    \uid, or $\CRED[\scid]$ to refer to a set of credentials with the
    identifiers in set \scid.
  \item[\OWNR.] Keeps track of which \uid is the owner of credentials obtained
    by honest users; i.e., $\OWNR[\cid]$ returns the \uid that obtained
    credential with identifier \cid.
  \item[\ATTR.] Keeps track of the attributes assigned to a credential, as well
    as the credential identifiers used to attest for any arbitrary claims
    required for issuance. This table can be indexed by credential identifier
    \cid.
  \item[\GRP.] Keeps track of the group to which a credential belongs to; i.e.,
    the group of the issuer who issued the credential. This table can be indexed
    by credential identifier \cid.
  \end{description}
\item[STables for signatures]:
  \begin{description}
  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
    of honest users.
  \item[\CSIG.] Maintains challenge signatures, generated via the \CHALb oracle,
    by one of the challenge users in the anonymity game.
  \end{description}
\end{description}

@@

        \procedure{$\ISSUE(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \\
          \hspace*{45pt}
          \Issue(\PRVIK[\gid],\PUBUK[\uid], \attrs,
          \ldblbrace \GK[\sgid] \rdblbrace) \rangle \\
          \trans[\cid] \gets \utrans;~\GRP[\cid] \gets \gid \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \attrs) \\
          \pcreturn \top \\          
        }

        \procedure{$\OBTAIN(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\attrs, 
          \ldblbrace \CRED[\scid] \rdblbrace), \\
          \hspace*{50pt} \adv \rangle \\
          \CRED[\cid] \gets \cred;~\GRP[\cid] \gets \gid \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \attrs) \\
          \pcreturn \top \\
        }

        \procedure{$\INSPECT(\gid,\sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\sig,\msg,\scid,\uattrs,\dattrs,\sgid)
          \in \SIG[\uid] \\
          \pcif \sig \in \CSIG: \pcreturn \bot \\
          (\y,\oproof) \gets
          \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\GK[\sgid]) \\
          \pcreturn (\y,\oproof)
        }

@@

        \procedure{$\OBTISS(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot:
          \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\attrs,
          \ldblbrace \CRED[\scid] \rdblbrace), \\
          \hspace*{60pt} \Issue(\PRVIK[\gid],\PUBUK[\uid],\attrs,
          \ldblbrace \GK[\sgid] \rdblbrace ) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid,\attrs) \\
          \GRP[\cid] \gets \gid \\
          \pcreturn \top \\
        }

        \procedure{$\SIGN(\uid,\msg,\feval,\ldblbrace\scid\rdblbrace )$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \cred \gets \CRED[\cid] \\
          \sig \gets \Sign(\PRVUK[\uid],\msg,\ldblbrace\CRED[\scid]\rdblbrace) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\sig,\msg,\feval,\scid) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\CHALb(\uid_{0,1},\msg,\feval,
          \ldblbrace (\cscid_{0,1},\sgid) \rdblbrace))$}{%          
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists \gid \in \sgid~\st~\gid \in \CO: \pcreturn \bot \\
          \pcif \feval(\PUBUK[\uid_0],\CRED[\scid_0],\msg) \neq \\
          \pcind \feval(\PUBUK[\uid_1],\CRED[\scid_1],\msg):
          \pcreturn \bot \\
          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\feval, \\
          \hspace*{42pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid_b]) \rdblbrace) \\
          \CSIG \gets \CSIG \cup
          \lbrace (\csig,\msg,\feval,\cscid_b,\sgid) \rbrace \\
          \pcreturn \csig
        }

@@

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS}(\parm) \\
    \sig \gets \Sign(\PRVUK[\uid],\msg,\feval,
    \ldblbrace \CRED[\scid] \rdblbrace ) \\
    \pcif \Verify(\sig,\msg,\GK[\sgid]) = 0: \pcreturn 1~
    \pccomment{\sig fails to verify} \\
    \pcif \CorrectIssue(\uid,\ldblbrace \scid \rdblbrace)
    = 0: \pcreturn 1~
    \pccomment{Some \cid should not have been issued} \\
    \pcif \CorrectEval(\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)
    = 0: \pcreturn 1~
    \pccomment{\msg should not have been signed}\\
    \pcif \CorrectInspect(\uid,\msg,\ldblbrace \scid \rdblbrace,
    \sig) = 0: \pcreturn 1~
    \pccomment{Some inspection of \sig is invalid}\\
    \pcreturn 0 \\
  }

  \procedure{$\CorrectIssue(\uid,\ldblbrace \scid \rdblbrace)$}{
    \forall \cid \in \scid~\textrm{parse}~\ATTR[\cid]~\textrm{as}~
    (\scid^\cid,\attrs^\cid) \\
    \forall \gid \in \GRP[\scid]~\textrm{parse}~\GK[\gid]~\textrm{as}~
    ((\cdot,\fissue^\gid),\cdot) \\        
    \pcif \exists \cid \in \scid, \gid \in \GRP[\scid]~\st~
    \fissue^\gid(\PUBUK[\uid],\attrs^\cid,\CRED[\scid]^\cid) = 0: 
    \pcreturn 0 \\
    \pcreturn 1 \\   
  }

  \procedure{$\CorrectEval(\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)$}{
    \pcif \feval(\PUBUK[\uid],\CRED[\scid],\msg) = 0: \pcreturn 0 \\
    \pcreturn 1 \\
  }

  \procedure{$\CorrectInspect(\uid,\msg,\ldblbrace \scid \rdblbrace, \sig)$}{
    \textrm{Let}~\sgid \gets \GRP[\scid];~
    \forall \gid \in \sgid~\textrm{parse}~\GK[\sgid]~\textrm{as}~
    (\cdot,(\cdot,\finsp^\gid)) \\
    \pccomment{\sig cannot be inspected by a suitable inspector} \\
    \pcif \exists \gid \in \sgid~\st~
    \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\GK[\sgid]) = \bot: \pcreturn 0 \\
    \pccomment{An $(\y,\iproof)$ pair is rejected by \Judge
      % \todo{This must be conditioned on \feval = 0!}
    } \\
    \pcif \exists \gid \in \sgid~\st~
    (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\GK[\sgid]) \land \\
    \pcind
    \Judge(\y,\iproof,\sig,\msg,\GK[\sgid]) = 0):
    \pcreturn 0 \\
    \pccomment{\y is the wrong value for some $\finsp^\gid$} \\
    \pcif \exists \gid \in \sgid~\st~
    \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\scid],\msg,\sig)): \pcreturn 0 \\
  }

@@

\paragraph{Anonymity.} %
In group signatures, anonymity captures that no adversary must be able to learn,
from any group signature, the identity (e.g., member index) of its signer. In 
anonymous credentials, it requires that no adversary should learn anything about
the holder of a successfully shown credential, beyond that he owns a credential
attesting for the claimed function of the attributes it contains. In both GS and
AC, it is also typically required that
multiple signatures/presentations by the users are unlinkable. The approach to
formally state this property is in both cases frequently the same: the adversary
picks two (honest) users (or credentials in the AC case), the game randomly
chooses one of them, and lets the adversary request challenge
signatures/presentations from it. The adversary wins if it succeeds in guessing
which was the chosen user/credential better than guessing at random. In group
signatures, the game must also restrict the adversary from opening challenge
signatures. In anonymous credentials, the game must further constraint the
adversary to output credentials that have some common function of (a subset of)
its attributes.

>>>>

\textcolor{red}{\textbf{WARNING:} The syntax and oracles below should be close
  to what we want. The game definitions should may be farther (especially
  traceability and non-frameability), but I'm having trouble with this level
  of abstraction without having some concrete scheme to consult on. Therefore,
  I'll start with a generic construction and then iterate the model again.
  Thus, note that the current modelling is, essentially, wrong.}

@@

@@

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. Hereafter, we assume that the
  public part \ipk is added to the group public key \gpk, as well as \fissue.
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers). Hereafter, we assume that the
  public part \opk is added to the group public key \gpk, along with \finsp.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\attrs,\ldblbrace (\gpk_i,\cred_i) \rdblbrace_{i \in \Issuers})
  \rangle$.] %
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred from an issuer in the system, on
  attribute set $\attrs$ plus, possibly, blinded attributes attested by
  previously obtained credentials $\cred_i$, from a multiset of other issuers
  (which may include the one to whom a new credential is being requested) with
  public keys $\gpk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\gpk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$\sig \gets \Sign(\gpk,\usk,\cred,\msg,\feval)$.]
  The user with with secret key \usk and credential \cred, produces a signature
  \sig over message \msg, meeting the conditions defined by \feval.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Checks whether \sig is a valid
  signature, over message \msg, from a user in the group with public key \gpk.
\item[$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg)$.] %
  Executed by the inspector with private key \osk. Receives a signature \sig
  over message \msg. If \trans contains a set of valid transcripts corresponding
  to the $\langle\Obtain,\Issue\rangle$ interactive protocol execution that
  issued the used to produce \sig, the function outputs a value $\y$ derived
  from the signer's public key, credential, message, and signature, as well as
  a proof of correct inspection. We sometimes abuse notation, and write
  $\trans[\uid]$ to mean that the \Inspect function is operating only for the
  obtain transcripts related to user \uid.
\item[$1/0 \gets \Judge(\gpk,\y,\iproof,\sig,\msg)$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \y,
  obtained by applying \Inspect to the the signature \sig over message \msg. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\upk, \attrs,\scred) \rightarrow 0/1$.] Defined by issuers,
  governs what customized conditions an issuer requires in order to issue
  credentials, when receiving a request from user with public key \upk, for
  attributes \attrs. \fissue may run checks on a (possibly empty) set of
  additional credentials \scred, which may further be used for blind issuance
  \commentwho{Jesus}{can it?}. \fissue returns $1$ to accept a request, $0$ to
  reject it.  
\item[$\feval: (\upk,\cred,\msg) \rightarrow 0/1$.] Can be defined by any party,
  although we anticipate that this will typically be done by either singers,
  verifiers, or some governance organization. It defines customized conditions
  to be met by the owner of a user key \upk and credential \cred, in
  order to sign a concrete message \msg. Returns $1$ to allow the signing,
  or $0$ to disallow it.
\item[$\finsp: (\upk,\cred,\msg) \rightarrow \bin^*$.] Defines what
  utility value, derived from the user's public key, credential, and message
  should be extractable by the group inspector.
\end{description}

@@

\begin{description}
\item[Tables for parties]:
  \begin{description}
  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
    i.e., they are sets of {\uid}s.
  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers.
    Since we assume only one issuer per group, they are sets of {\gid}s.
  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) inspectors.
    Since we assume only one inspector per group, they are sets of {\gid}s.
  \end{description}
\item[Tables for keys]:
  \begin{description}
  \item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$.
    To refer to the key pair of a specific user, we use $\UK[\uid]$. \PUBUK
    is a shorthand to refer to the public part, and \PRVUK refers to the
    private part -- we may also index both by \uid.
  \item[\IK, \PUBIK and \PRVIK.] Same as \UK, but for issuer key pairs. In
    addition, \IK also includes the \fissue function, which is part of the
    public key.
  \item[\OK, \PUBOK, \PRVOK.] Same as \UK, but for inspector key pairs. In
    addition, \OK also includes the \finsp function, which is part of the
    public key.
  \item[\GK.] We bundle public keys for issuers and inspectors into a common
    public key for each group. We use the table \GK for that purpose which,
    consequently, can also be indexed by \gid.
  \end{description}
\item[Tables for credentials-related data]:
  \begin{description}
  \item[\CRED.] Stores information related to credentials obtained by honest
    users. Thus, it is indexable by \cid. More specifically, it stores tuples of
    the form $(\uid,\cred,\gid,\attrs,\scid)$, where \uid is the identity of the
    owner of the credential, \cred (when available) is the credential itself,
    \gid is the identifier of the group to which the credential belongs, \attrs
    are the attributes included in \cred, and \scid are the identifiers of any
    additional credential that \uid used to request \cred.
  \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
    ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
  \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
    ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
  \item[\GRP.] For notational convenience, when we write $\GRP[\cid]$ we mean
    ``\gid such that $\CRED[\cid] = (\cdot, \gid, \cdot, \cdot, \cdot)$''.
  \end{description}
\item[Tables for signatures]:
  \begin{description}
  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
    of honest users.
  \item[\CSIG.] Maintains challenge signatures, generated via the \CHALb oracle,
    by one of the challenge users in the anonymity game.
  \end{description}
\end{description}

@@

        \procedure{$\ISSUE(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\          
          \pcif \gid \notin \HI: \pcreturn \bot \\
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \\
          \hspace*{45pt}
          \Issue(\PRVIK[\gid],\PUBUK[\uid], \attrs,
          \ldblbrace \CRED[\scid] \rdblbrace) \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cdot, \gid, \attrs, \scid) \\
          \pcreturn \top \\          
        }

        \procedure{$\OBTAIN(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\attrs, 
          \ldblbrace \CRED[\scid] \rdblbrace), \\
          \hspace*{50pt} \adv \rangle \\
          \CRED[\cid] \gets (\uid, \cdot, \gid, \attrs, \scid) \\          
          \pcreturn \top \\
        }

        \procedure{$\INSPECT(\gid,\sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\cid,\sig,\msg,\feval)
          \in \SIG[\uid] \\
          (\y,\iproof) \gets
          \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg) \\
          \pcif \CSIG[\sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\sig_{1-b},\msg,\feval)$} \\
          \pcind (\y_{1-b},\iproof_{1-b}) \gets
          \Inspect(\GK[\gid],\PRVOK[\gid],\\
          \hspace*{107pt} \trans,\sig_{1-b},\msg) \\
          \pcind \pcif \y_{1-b} \neq \y: \pcreturn \bot \\
          \pcreturn (\y,\iproof)
        }

@@

        \procedure{$\OBTISS(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot:
          \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\attrs,
          \ldblbrace \CRED[\scid] \rdblbrace), \\
          \hspace*{60pt} \Issue(\PRVIK[\gid],\PUBUK[\uid],\attrs,
          \ldblbrace \CRED[\scid] \rdblbrace ) \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cred, \gid, \attrs, \scid) \\
          \pcreturn \top \\
        }

        \procedure{$\SIGN(\uid,\cid,\msg,\feval)$}{%
          \pcif \uid \notin \HU \lor \CRED[\cid] = \bot: \pcreturn \bot \\
          \sig \gets \Sign(\GK[\GRP[\cid]],\PRVUK[\uid],\msg,\CRED[\cid]) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\cid,\sig,\msg,\feval) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\CHALb(\cuid_{0,1},\ccid_{0,1},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \gid = \GRP[\ccid_0] \neq \GRP[\ccid_1]: \pcreturn \bot \\
          \pcif \gid \in \CO: \pcreturn \bot \\
          \pcif \feval(\PUBUK[\uid_0],\CRED[\scid_0],\msg) \neq \\
          \pcind \feval(\PUBUK[\uid_1],\CRED[\scid_1],\msg):
          \pcreturn \bot \\
          \csig_b \gets \Sign(\GK[\gid],\PRVUK[\cuid_b],\CRED[\ccid_b],
          \msg,\feval) \\
          \csig_{1-b} \gets \Sign(\GK[\gid],\PRVUK[\cuid_{1-b}],\CRED[\ccid_{1-b}],
          \msg,\feval) \\          
          \CSIG[\csig_b] \gets 
          \lbrace (\csig_{1-b},\msg,\feval) \rbrace \\
          \pcreturn \csig_b
        }

@@

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\cid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS}(\parm) \\
    \sig \gets \Sign(\GK[\cid],\PRVUK[\uid],\cid,\msg,\feval) \\
    \pcif \Verify(\GK[\cid],\sig,\msg) = 0: \pcreturn 1~
    \pccomment{\sig fails to verify} \\
    \pcif \CorrectIssue(\uid,\cid) = 0: \pcreturn 1~
    \pccomment{\cid should not have been issued} \\
    \pcif \CorrectEval(\uid,\cid,\msg,\feval)
    = 0: \pcreturn 1~
    \pccomment{\msg should not have been signed}\\
    \pcif \CorrectInspect(\uid,\cid,\msg,\sig) = 0: \pcreturn 1~
    \pccomment{Some inspection of \sig is invalid}\\
    \pcreturn 0 \\
  }

  \procedure{$\CorrectIssue(\uid,\cid)$}{
    \gid \gets \GRP[\cid] \\
    \textrm{Parse}~\ATTR[\cid]~\textrm{as}~(\attrs^\cid,\scid^\cid);~
    \textrm{Parse}~\GK[\gid]~\textrm{as}~
    ((\cdot,\fissue^\gid),\cdot) \\        
    \pcif \fissue^\gid(\PUBUK[\uid],\attrs^\cid,\CRED[\scid]^\cid) = 0: 
    \pcreturn 0 \\
    \pcreturn 1 \\   
  }

  \procedure{$\CorrectEval(\uid,\cid,\msg,\feval)$}{
    \pcif \feval(\PUBUK[\uid],\CRED[\cid],\msg) = 0: \pcreturn 0 \\
    \pcreturn 1 \\
  }

  \procedure{$\CorrectInspect(\uid,\cid,\msg,\sig)$}{
    \textrm{Let}~\gid \gets \GRP[\cid];~
    \textrm{Parse}~\GK[\gid]~\textrm{as}~(\cdot,(\cdot,\finsp^\gid)) \\
    \pccomment{\sig cannot be inspected} \\
    \pcif \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg) = \bot: \pcreturn 0 \\
    \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge
      % \todo{This must be conditioned on \feval = 0!}
    } \\
    \pcif (\y,\iproof) \gets \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg)
    \land
    \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 0): \\
    \pcind \pcreturn 0 \\
    \pccomment{\y is the wrong value} \\
    \pcif \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\cid],\msg)):
    \pcreturn 0 \\
    \pcreturn 1
  }

@@

\paragraph{Anonymity.} %
In group signatures, anonymity captures that no adversary must be able to learn,
from any group signature, the identity (e.g., member index) of its signer. In 
anonymous credentials, it requires that no adversary should learn anything about
the holder of a successfully shown credential, beyond that he owns a credential
attesting for the claimed predicate of the attributes it contains. In both GS
and AC, it is also typically required that
multiple signatures/presentations by the users are unlinkable. The approach to
formally state this property is in both cases frequently the same: the adversary
picks two (honest) users (or credentials in the AC case), the game randomly
chooses one of them, and lets the adversary request challenge
signatures/presentations from it. The adversary wins if it succeeds in guessing
which was the chosen user/credential better than guessing at random. In group
signatures, the game must also restrict the adversary from opening challenge
signatures. In anonymous credentials, the game must further constraint the
adversary to output credentials that both meet the same (challenge) predicate
of their attributes.

In our notion of anonymity for \UAS, we need to merge the previous constraints.
Furthermore, a key difference with group signatures is that the game requires
the adversary to output credential identifiers, rather than user identifiers.
Specifically, this means that the adversary may actually output two credentials
that belong to the same user. Therefore, in some sense, the anonymity we get is
more general than that of group signatures. Moreover, in order to prevent
trivial wins by the adversary, we have to restrict that the challenge signatures
belong to a group that has been ``programmed'' with the same evaluation and
inspection functions, which is again a generalization over group signatures,
as discussed in the sequel. Other than this, the overall approach is the same:
the adversary picks two honestly obtained credentials, and one of them (set
by the $b$ value defining the $anon-b$ game) is used to program the \CHALb
oracle. The formal specification of the anonymity game is
given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,\CU\rbrace
\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN,
\INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace
\GEN,\lbrace\II,\OO\rbrace,\CORR,\OBTAIN,\SIGN,\INSPECT,\CHALb)$

\begin{figure}[htp!]
  \procedure{$\ExpAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ccid_0,\ccid_1,\status) \gets \adv^{\Oanonc}(\choose,\parm) \\
     b^* \gets \adv^{\Oanong} (\guess,\status) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure}
